Bayesian integration of networks without gold standards

### 2011-08-20 src/main/latex/paper/paper.tex
moved description of priors to earlier position in text

@@

The second step in each cycle is the sampling of a new error rate vector $\theta$ based on $G$. The error rates $\alpha_i$ and $\beta_i$ behave like the success rates for misreading each potential edge. Modelling each observation event over a potential edge as a Bernoulli experiment with such a success rate, the number of false positives and false negatives in an experimental graph $X_i$ would follow a binomial distribution. The success rates for a binomial distribution can be sampled using the Beta distribution. The Beta distribution takes two parameters, $a$ and $b$. The parameters $a$ and $b$ can be interpreted as one plus the number of successes and failures, respectively, in a binomial distributed dataset. In order to obtain values for $a$ and $b$, one can compare each $X_i$ to the currently assumed true graph $G$ and use it to count the number of supposed True Positives (tp), False Positives (fp), True Negatives (tn) and False Negatives (fn). Then, the full conditionals for $\alpha$ and $\beta$ can be sampled as follows:
\begin{align}
  \alpha_i &\sim Be(\text{fp}_i+1, \text{tn}_i+1)\\
  \beta_i &\sim Be(\text{fn}_i+1, \text{tp}_i+1)
\end{align}

@@

%Finally, a score analogous to the likelihood of the current state can be computed as $\pi(\theta,G|X)$.
%Lacking a way to determine this value directly, one may exploit the following equation.

%\begin{equation} 
%	 \pi(\theta,G|X) = \frac{\pi(\theta,G,X)}{\prob(X)} 
%\end{equation}

%Thus, the posterior distribution $\pi(\theta,G|X)$ is proportional to the joint distribution $\pi(\theta,G,X)$. The joint distribution may in turn be determined as follows.

%\begin{equation} 
%	 \pi(\theta,G,X) = \pi(G)\cdot\pi(\theta)\cdot\prob(X|\theta,G)
%\end{equation}

%In summary, the following statement can be made.

%\begin{equation} 
%	 \pi(\theta,G|X) \propto \pi(G)\cdot\pi(\theta)\cdot\prob(X|\theta,G) 
%\end{equation}

%As a consequence, three values need to be determined: the prior distribution $\pi(G)$, the prior distribution $\pi(\theta)$ and the likelihood $\prob(X|\theta,G)$.

@@

>>>>

To determine the joint posterior distribution $\pi(\theta,G|X)$,  one may exploit the following equation:

\begin{equation} 
	 \pi(\theta,G|X) = \frac{\pi(\theta,G,X)}{\prob(X)} 
\end{equation}.

Thus, the posterior distribution $\pi(\theta,G|X)$ is proportional to the joint distribution $\pi(\theta,G,X)$. The joint distribution may in turn be determined as follows.

\begin{equation} 
	 \pi(\theta,G,X) = \pi(G)\cdot\pi(\theta)\cdot\prob(X|\theta,G)
\end{equation}

In summary, the following statement can be made.

\begin{equation} 
	 \pi(\theta,G|X) \propto \pi(G)\cdot\pi(\theta)\cdot\prob(X|\theta,G) 
\end{equation}

As a consequence, three values need to be determined: the prior distribution $\pi(G)$, the prior distribution $\pi(\theta)$ and the likelihood $\prob(X|\theta,G)$.

We define the prior distribution of $\pi(G)$ based on the prior probability of each single edge to exist:
\begin{align}
  \pi(G) &= \prod_{e \in \binom{V}{2}} \pi(G_e)\\
         &= (1-q)^{\left |\binom{V}{2}\setminus E_G \right |} \cdot q^{|E_G|}
\end{align},
where $q$ is the prior probability of an edge to really exist. \note{Not sure we really need this, since we don't use it afterwards anywhere.}

To determine the prior distribution $\pi(\theta)$, we have to consider the nature of the error rates $\alpha_i$ and $\beta_i$ as ``success rates'' for misreading each potential edge. Modelling each observation event over a potential edge as a Bernoulli experiment with such a success rate, the number of false positives and false negatives in an experimental graph $X_i$ would follow a binomial distribution. The success rates for a binomial distribution can be sampled using the Beta distribution. The Beta distribution is dependent on two parameters, $a$ and $b$.

@@

The second step in each cycle is the sampling of a new error rate vector $\theta$ based on $G$. 
%FIXME
The parameters $a$ and $b$ can be interpreted as one plus the number of successes and failures, respectively, in a binomial distributed dataset. In order to obtain values for $a$ and $b$, one can compare each $X_i$ to the currently assumed true graph $G$ and use it to count the number of supposed True Positives (tp), False Positives (fp), True Negatives (tn) and False Negatives (fn). Then, the full conditionals for $\alpha$ and $\beta$ can be sampled as follows:
\begin{align}
  \alpha_i &\sim Be(\text{fp}_i+1, \text{tn}_i+1)\\
  \beta_i &\sim Be(\text{fn}_i+1, \text{tp}_i+1)
\end{align}.

@@

%Finally, a score analogous to the likelihood of the current state can be computed as $\pi(\theta,G|X)$.

@@

\note{TODO: Fix capitalization and italics in BibTeX file}
